---
title: "Diamond Price Prediction"
author: "Dr. Kaung Myat Khant"
date: "`r Sys.Date()`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = "")
library(ggplot2)
library(plotly)
library(dplyr)
library(knitr)
```

## About this App

This app can be used to predict the price of a diamond based on its colour, clarity and mass in carat. You can also specify which cut of the diamonds you want to use as a dataset in predicting the price.

```{r data, include = TRUE}
data <- diamonds %>% select(cut, color, clarity, carat, price) 
data %>% slice_head(n= 5)  %>%   kable()
```

## How to use the app

You can access the application here:   
https://8odfh6-kmk-27.shinyapps.io/predictdiamondprice

You can access the files for the application in the following github repository:  
https://github.com/kaungMyat-Khant/Shiny-Course-project.git  

#### Steps to use the app 

1. First, select the cuts of the diamonds to define the dataset to use.  

2. Then, select the colour, clarity and mass (carat) of the diamond you want to predict the price.  

3. Click **Predict** button.

## Properties of diamonds (Inputs) used to predict the price

```{r input}
Carat <- plot_ly(data = data, x = ~carat,name = "Carat", type = "box")
Colour <- plot_ly(data = data, x = ~color,name = "Colours")
Clarity <- plot_ly(data = data, x = ~clarity,name = "Clarity")
Cut <- plot_ly(data = data, x = ~cut,name = "Cuts")
subplot(Cut, Colour, Clarity, Carat, nrows = 2)
```

## Output  

```{r output}
fit <- lm(price ~ carat+color+clarity, data = data, subset = cut == "Ideal")
abline <- predict(fit, newdata = data)
result <- predict(fit, newdata = data.frame(carat = 0.7, color = "J", 
                                            clarity = "IF"))
plot <- data %>% 
    filter(cut=="Ideal") %>% 
    ggplot(aes(carat, price))+
    geom_point(colour = "skyblue", alpha = 0.3, size = 1.5)+
    geom_abline(slope = coef(fit)[2], intercept = coef(fit)[1], 
                color = "firebrick", size = 2)+
    geom_point(data = data.frame(carat = 0.7, price = result), aes(carat,price),
               colour = "forestgreen", size = 10, alpha = 0.9)+
    labs(
        title="Price predicted by carat, colour and clarity",
        subtitle = "Data of ideal cuts",
        x = "Mass carat",
        y = "Price(US$)"
    )+ theme_minimal()
ggplotly(plot)
```

